\nointent
\ProjectTitle{Food Delivery Application (2024 | Group) \hfill \href{https://uchihaithachi.github.io/cv/arch/food_delivery.png}{\textbf{Architecture}} \enspace|\enspace \href{https://github.com/FoodDeliveryApp-ISA}{\textbf{Github} \faGithub}}

\nointent
Built a scalable, event-driven food delivery platform inspired by systems like Uber Eats, using a modern microservices architecture. As part of the core team, I focused on designing and developing the Restaurant Service.

\begin{itemize}
    \item Developed the Restaurant Module with secure sign-up/login using \textbf{Spring Security} and \textbf{JWT} (with extended claims).
    \item Built CRUD APIs for menu and item management; integrated \textbf{Redis caching} to improve performance and reduce database load, with appropriate cache invalidation strategies.
    \item Enabled order sync via \textbf{Kafka}: when an order is placed, an event is published to the `order\_created` topic, which the restaurant service consumes to update order details.
    \item Implemented real-time order state updates through Kafka's publish/subscribe model to keep restaurant and rider services in sync.
    \item Integrated \textbf{WebSockets} for real-time restaurant notifications (e.g., new orders, rider assignments).
    \item Built a secure "Forget Password" flow using time-sensitive tokens for authentication recovery.
    \item Implemented robust exception handling and API protection through middleware guards and JWT verification.
    \item Dockerized all components (frontend, backend, Kafka, Redis, PostgreSQL) and managed them via \textbf{Docker Compose}.
    \item Worked in Agile sprints using \textbf{Jira} for task tracking and \textbf{Bitbucket} for version control.
\end{itemize}

\nointent
\textit{Keywords:} Java, Spring Boot, gRPC, Kafka, Redis, PostgreSQL, WebSocket, Docker, React.js, Ant Design

\vspace{1em}
