\noindent
\textbf{Co-founder \& Lead Engineer} \hfill \textit{Jan 2026 -- Present}\\
\noindent
\textit{ScaleX --- SaaS Development Lab} \hfill \textit{Remote / Sri Lanka}\\[0.05em]
\begin{itemize}[leftmargin=*, itemsep=0.3em, topsep=0.01em]
    \item \textbf{Stream-Native Tipping Platform:} Architecting a creator-focused SaaS to solve Sri Lankan payout barriers by integrating PayHere's aggregated gateway. Developed an OBS-native alert system using webhook-driven \texttt{notify\_url} callbacks to trigger real-time on-stream overlays.
    \item \textbf{High-Performance Scheduling SaaS:} Engineering a mobile-first scheduling tool using Next.js 14 and Supabase Realtime for live heatmap synchronization. Implemented a custom best-slot recommendation algorithm to rank optimal meeting times based on participant overlap and duration constraints.
    \item \textbf{Scalable Infrastructure \& DevOps:} Designed a \$0-to-launch deployment strategy leveraging Vercel serverless functions and Supabase PostgreSQL with connection pooling. Established robust security protocols including Zod-based input validation and rate-limiting to ensure system resilience.
    \item \textbf{Strategic Compliance \& Growth:} Navigating CBSL regulatory frameworks to operate as a software platform while delegating fund-handling to licensed gateways to minimize operational risk. Implementing a ``freemium'' viral loop strategy with branded footers and Stripe-integrated Pro tiers for monetization.
    \item \textbf{AgriNova:} Developing an automated inventory management and IoT-driven tracking system for agricultural supply chains, focusing on resource optimization and real-time monitoring.
\end{itemize}
