\noindent
\textbf{Software Engineer Intern} \hfill \textit{Dec 2024 -- May 2025}\\
\noindent
\textit{Information Systems Associates (Pvt) Ltd --- Aviation Technology(Airarabia)}\\[0.05em]
\begin{itemize}[leftmargin=*, itemsep=0.3em, topsep=0.01em]
    \item \textbf{AeroOrder --- Order Management Microservice (Java 17, Spring Boot, Gradle)}
    \begin{itemize}[leftmargin=1.5em, itemsep=0.1em]
        \item Engineered a distributed, Kafka-backed ID generator for Passenger Name Records (PNRs), ensuring uniqueness and security across scaled instances.
        \item Optimized PNR generation to achieve \textbf{25+ PNRs/sec throughput} per node with \textbf{<100ms latency}, validated via \textbf{Apache JMeter} stress testing.
        \item Resolved production \textbf{Kafka consumer lag} by implementing robust shutdown hooks and enhanced retry mechanisms.
        \item Established a monitoring stack using \textbf{Prometheus} and \textbf{Grafana} to visualize queue time and latency for asynchronous loads.
        \item Refactored \textbf{Kafka Streams} logic into a Producer-Consumer model, significantly reducing consumer lag and improving stability.
    \end{itemize}
    
    \item \textbf{AeroMart — Legacy Passenger Reservation System (Java 8, Ant)}
    \begin{itemize}[leftmargin=1.5em, itemsep=0.1em]
        \item Integrated \textbf{gRPC} clients and \textbf{Kafka} consumers into a \textbf{Java 8 monolith}, enabling backward-compatible communication with new microservices.
        \item Developed database-driven \textbf{feature toggles} to manage PNR routing logic, allowing for granular control during production rollout.
    \end{itemize}

    \item \textbf{Collaboration \& Engineering Standards}
    \begin{itemize}[leftmargin=1.5em, itemsep=0.1em]
        \item Authored technical design documents, sequence diagrams, and integration plans on Confluence.
        \item Participated in code reviews and Agile ceremonies to deliver production-ready features using \textbf{Jira} and \textbf{Bitbucket}.
    \end{itemize}
\end{itemize}

\vspace{-0.1em}
\noindent\small
\textsc{Keywords:} Java 17/8, Spring Boot, gRPC, Kafka, Kafka Streams, Docker, Prometheus, Grafana, JMeter, Oracle DB, Microservices, Distributed Systems, Time-Series Data.
\normalsize