\noindent
\textbf{Software Engineer Intern} \hfill \textit{Dec 2024 -- May 2025}\\
\textit{Information Systems Associates (Pvt) Ltd --- Aviation Technology} \hfill \textit{Colombo, Sri Lanka (On-site)}
\begin{itemize}[leftmargin=*, itemsep=0.2em, topsep=0.1em]
    \item \textbf{AeroOrder --- Order Management Microservice (Java 17, Spring Boot, Gradle)}
    \begin{itemize}[leftmargin=1.5em, itemsep=0.05em]
        \item Built a distributed, Kafka-backed PNR ID generator ensuring uniqueness across scaled instances.
        \item Optimized PNR generation to \textbf{25+ PNRs/sec} with \textbf{<100ms latency}, validated via \textbf{JMeter} stress tests.
        \item Fixed production \textbf{Kafka consumer lag} using robust shutdown hooks and enhanced retry mechanisms.
        \item Deployed \textbf{Prometheus} and \textbf{Grafana} monitoring to visualize queue time and latency metrics.
        \item Refactored \textbf{Kafka Streams} logic into a Producer-Consumer model, reducing lag and improving stability.
    \end{itemize}
    
    \item \textbf{AeroMart — Legacy Passenger Reservation System (Java 8, Ant)}
    \begin{itemize}[leftmargin=1.5em, itemsep=0.05em]
        \item Integrated \textbf{gRPC} and \textbf{Kafka} into a \textbf{Java 8 monolith} for backward-compatible microservices sync.
        \item Implemented database-driven \textbf{feature toggles} for granular PNR routing control during rollout.
    \end{itemize}

    \item \textbf{Collaboration \& Engineering Standards}
    \begin{itemize}[leftmargin=1.5em, itemsep=0.05em]
        \item Produced design docs and sequence diagrams; participated in code reviews and Agile ceremonies via \textbf{Jira/Bitbucket}.
    \end{itemize}
\end{itemize}

\vspace{-0.2em}
\noindent\small
\textsc{Keywords:} Java 17/8, Spring Boot, gRPC, Kafka, Docker, Prometheus, Grafana, JMeter, Oracle DB, Microservices.
\normalsize